---
output:
  word_document: default
  html_document: default
---
# Ben Robison
## Mod6- Clustering

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
```

```{r}
trucks <- read_csv("trucks.csv")
View(trucks)
```

```{r}
ggplot(trucks, aes(x=Distance, y=Speeding))+
  geom_point()
```

Clear clustering, trend seems to be more distance, more likely to speed a higher percentage of time. 

```{r}
truck2 = select(trucks, -Driver_ID) 
truck2 = as.data.frame(scale(truck2)) 
```

```{r}
set.seed(1234)
clusters1 <- kmeans(truck2, 2)
fviz_cluster(clusters1, truck2)
```
Clustered as expected, 3820 in middle might be issue. 2 clusters seems appropriate though 3 could be better for top right side.

```{r}
set.seed(123)
fviz_nbclust(truck2, kmeans, method = "wss")
```

```{r}
set.seed(123)
fviz_nbclust(truck2, kmeans, method = "silhouette")
```
Yes the 3 to 4 range appears to be the optimal number of clusters
```{r}
set.seed(1234)
clusters2 <- kmeans(truck2, 4)
fviz_cluster(clusters2, truck2)
```

Clusters 1 and 2 are most likely people who speed rarely if at all. While cluster 3 is people who speed consistenly for a long duration, similar to cluster 4 who speed consistenly for a short duration. 3 and 4 would probably have some overlap if data was taken more than once for each driver.

```{r}
wine <- read_csv("wineprice.csv")
View(wine)
wine2 = wine %>% select(c(-Year, -FrancePop)) 
wine2 =as_data_frame(scale(wine2))
```

```{r}
set.seed(123)
fviz_nbclust(wine2, kmeans, method = "wss")
```
```{r}
set.seed(123)
fviz_nbclust(wine2, kmeans, method = "silhouette")
```
WSS method seems to favor closer to 4 while silhouette method favors closer to 5 it appears.

```{r}
set.seed(1234)
clusters3 <- kmeans(wine2, 5)
fviz_cluster(clusters3, wine2)
```

```{r}
m = c( "average", "single", "complete", "ward")
names(m) = c( "average", "single", "complete", "ward")

ac = function(x) {
  agnes(wine2, method = x)$ac
}
map_dbl(m, ac)
```

```{r}
hc = agnes(wine2, method = "ward")
pltree(hc, cex = 0.6, hang = -1, main = "Agglomerative Dendrogram") 
plot(hc, cex.axis= 0.5) 
rect.hclust(hc, k = 5, border = 2:6) 

```

```{r}
hc2 = diana(wine2)
pltree(hc2, cex = 0.6, hang = -1, main = "Divisive Dendrogram") 
plot(hc2, cex.axis= 0.5) 
rect.hclust(hc2, k = 5, border = 2:6) 
```

